### 2022-08-25 msred-geometry.tex
Updated slides for ESI talk.

	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \circ \mu_j = 0$$
	employing the so-called \emph{ Richardson-Nijenhuis product}
		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i\circ\mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.

@@

	\begin{defblock}[Leibniz algebra of observables]
		\hspace{.25em} $Leib(M,\omega)$ is given by:
		\begin{itemize}
			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
			\item[•] with the binary bracket 
			\begin{center}
				\includestandalone{Pictures/Equation_Leibbracket}	
			\end{center}
		\end{itemize}	
	\end{defblock}
	\vfill
	\pause
	%
	\begin{propblock}
		\begin{itemize}
			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket = 
			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
			+
			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
		\end{itemize}
	\end{propblock}

>>>>

	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
	employing the so-called \emph{ Richardson-Nijenhuis product}
		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.

@@

	\begin{defblock}[Leibniz algebra of observables]
		\hspace{.25em} $Leib(M,\omega)$ is given by:
		\begin{itemize}
			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
			\item[•] with the binary bracket 
			\begin{center}
				\includestandalone{Pictures/Equation_Leibbracket}	
			\end{center}
		\end{itemize}	
	\end{defblock}
	\vfill
	\pause
	%
	\begin{propblock}
		\begin{itemize}
			\setlength\itemsep{1em}
			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
			+
			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
		\end{itemize}
	\end{propblock}
